\documentclass[]{article}

% Margins
\usepackage[letterpaper, top=1in, bottom=1in, left=1in, right=1in]{geometry}

% For prettier tables
\usepackage{array}

% For pictures
\usepackage{graphicx}

% For units
\usepackage{siunitx}

% Clickable Table of Contents
\usepackage{color}   %May be necessary if you want to color links
\usepackage{hyperref}
\hypersetup{
	colorlinks=true, %set true if you want colored links
	linktoc=all,     %set to all if you want both sections and subsections linked
	linkcolor=black,  %choose some color if you want links to stand out
}

% For enumerates
\usepackage{enumitem}

% For code
\usepackage{courier}
\usepackage{listings}
\lstset{ mathescape }
\lstset{basicstyle=\ttfamily\footnotesize,breaklines=true}

% Change Font
\usepackage[sfdefault]{roboto}  %% Option 'sfdefault' only if the base font of the document is to be sans serif
\usepackage[T1]{fontenc}

% For Header
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{fancyhdr}

% Make Header
\pagestyle{fancy}
\rhead{Andrews, Hickey}
\lhead{CS 467}

% Page numbers
\pagenumbering{arabic}

% Title
\title{Machine Learning Proposal}
\author{Ben Andrews \& Jimmy Hickey}

\begin{document}
	\maketitle

Our goal is to create an AI to play Connect 4. We will use many of the ideas that we learned in class such as supervised and unsupervised learning as well as some ideas from our Artificial Intelligence course. We will design mulitple different algorithms using Python to play the game. They will be able to play against humans as well as each other. Our hope is that our AIs will quickly learn to outplay human players. We will train it by playing games ourselves.

Connect 4 is a two player board game. The game board consist of a 7x6 matrix of holes. Players alternate between placing a piece in a column, falling to the lowest open hole in that column. A player wins by connecting four of their pieces horizontally, vertically, or diagonally. 

We have done some cursory research into past attempts to solve this problem. We know that it has been solved, but we still think there is value in pairing these different methods against each other.

We hope to determine which method works best for solving this problem. Our presentation will include live demonstrations as well as algorithmic analysis of our methods.

\section*{References}
\href{https://tromp.github.io/c4/c4.html}{John's Connect Four Playground}

\end{document}
